Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-27 journal/article.tex
T: Supporting tools

Even if any activities aiming for transformation can be considered as
investments in themselves, the transformation process included specific
investments in some tangible entities. These investments were focused on better
enabling agile software development. Typical investments were new management
tools, improvements in testing environments, and updating of the physical
working spaces. Table \ref{table:transformation_investments} summarizes common
types of investments.

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        Investment for transformation      &  Described in  \\
        \midrule
        Proprietary agile material or documentation   & 
                P1, P2, P8, P14, P16, P23, P26, P29, P32, P45  \\
        Refurbishing work areas and other spaces   &
                P6, P22, P35, P36, P38, P42, P46, P48 \\
        \bottomrule
    \end{tabular}
    \caption{Activities in the organization aiming to create change}
    \label{table:transformation_investments}
\end{table}

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ l l }
        \toprule
        Factors of investment and resourcing  &  Described in \\
        \midrule
        Lack of coaching                      &  P1, P6, P23, P45, P47, P49  \\
        Lack of training                      &  P11, P20, P45  \\
        Excessive commitment of people        &  P37, P42, P49  \\
        Old commitments are kept              &  P11, P21  \\
        Physical spaces can not be rearranged  &  P6, P29, P36, P38, P49  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of investment and resourcing factors that affect
             transformation negatively}
    \label{table:challenges_lackofinvestment}
\end{table}

@@

In some cases the old way of working had people seated physically distributed,
in opposite to what agile methods typically suggest. Office spaces needed to be
arranged so that the entire team could work in a single room, but it took time
and effort, and it was not always possible [P6, P36, P38]. Lewis and Neher describe
how dedicated rooms for teams could not be arranged, and team events such as
daily stand-ups required booking a conference room [P29]. In another case the
estate organization shut down the teams' attempts to modify working spaces
[P49].

>>>>

Even if any activities aiming for transformation can be considered as
investments in themselves, the transformation process included specific
investments in some tangible entities. These investments were focused on better
enabling agile software development, and highlight the concerns that
organizations had when implementing an agile model. Typical investments were new
management tools, improvements in testing environments, and updating of the
physical working spaces. Table \ref{table:transformation_investments} summarizes
common types of investments.

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.42\textwidth}
                     >{\raggedright\arraybackslash}p{0.50\textwidth} }
        Investment for transformation      &  Described in  \\
        \midrule
        Agile project management tools  &
                P10, P11, P14, P16, P17, P26, P33,
                P41, P43, P44, P45, P48, P50 \\
        Proprietary agile material or documentation   & 
                P1, P2, P8, P14, P16, P23, P26, P29, P32, P45  \\
        Refurbishing work areas and other spaces   &
                P6, P22, P35, P36, P38, P42, P46, P48 \\
        \bottomrule
    \end{tabular}
    \caption{Investments aiming to make agile methods perform better}
    \label{table:transformation_investments}
\end{table}

% Agile development tools

Using and investing in software tools supporting agile development was mentioned
in several studies. Especially project management tools were discussed.
Some reasons for introducing new project management tools was that spreadsheets
became unmanageable [P16], and the status overview of agile projects was lacking
[P17]. When a suitable agile tool was implemented it was attributed for better
visibility [P26, P33]. Using a project management tool can also help in teaching
the particularities of the new process [P14].

It was typical to use web-based tools for project manangement [P10, P11, P16].
The use of web based tools such as wiki pages was also attributed to lessen the
effort in documentation [P14]. Other tools that were taken into use while
implementing agile methods were teleconferencing tools [P11], discussion forums
for contacting coaches [P41], and information radiators to raise the awareness
of the new method [P22, P41]. Also development and delivery infrastructure
required investments to match the needs of agile development [P50].

Several organizations created their own tools for managing agile development
[P10, P11, P26]. Especially companies developing management software, such as
SAP, Primavera, and Salesforce, customized their product to support the agile
model being implemented [P16, P44, P45]. The development of the tools themselves
also served as a showcase of agile delivery [P10, P45].

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ l l }
        \toprule
        Factors of investment and resourcing  &  Described in \\
        \midrule
        Lack of coaching                      &  P1, P6, P23, P45, P47, P49  \\
        Lack of training                      &  P11, P20, P45  \\
        Excessive commitment of people        &  P37, P42, P49  \\
        Old commitments are kept              &  P11, P21  \\
        Physical spaces can not be rearranged  &  P6, P14, P29, P36, P38, P49  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of investment and resourcing factors that affect
             transformation negatively}
    \label{table:challenges_lackofinvestment}
\end{table}

@@

In some cases the old way of working had people seated physically distributed,
in opposite to what agile methods typically suggest. Office spaces needed to be
arranged so that the entire team could work in a single room, but it took time
and effort, and it was not always possible [P6, P14, P36, P38]. Lewis and Neher
describe how dedicated rooms for teams could not be arranged, and team events
such as daily stand-ups required booking a conference room [P29]. In another
case the estate organization shut down the teams' attempts to modify working
spaces [P49].
